---
title: 'Assignment 2'
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
# Loading data
data(CPS85, package = "mosaicData")

df <- CPS85 %>%
  group_by(sector, sex) %>%
  summarise(n = n())

print(df)
```
Q1: Construct a stacked bar chart to show the number of females and males in each sectors.

Hint: `geom_text()` may help you show the numbers in the bars.
The two color values `#C73C68` and `#B6C468` can help.
```{r}
ggplot(df, aes(y = reorder(sector, n, sum, decreasing = TRUE), x = n, fill = sex)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = n), position = position_stack(vjust = 0.5), color = "black", size = 3) +
  labs(
    x = "Number of persons",
    y = ""
  ) +
  scale_fill_manual(values = c("F" = "#C73C68", "M" = "#B6C468"))
# + theme_minimal()
```
Q2: Based on the dataset `SaratogaHouses` from package `mosaicData`,
please draw a scatterplot for house ages and prices with quadratic line of best fit.

Hint: `geom_smooth()` may help you to construct the linear regression line.
You can specify the points with `size = 1`, `alpha = 0.4`,
the fitting line with `size = 0.5`, `color = "tomato"`.
```{r}
library(mosaicData)
data(SaratogaHouses)

ggplot(SaratogaHouses, aes(x = age, y = price)) +
  geom_point(size = 1, alpha = 0.4, color = "cornflowerblue") +
  geom_smooth(method = "lm", formula = y ~ poly(x, 1), se = TRUE, size = 0.5, color = "tomato") +
  labs(
    title = "Age vs. Price",
    subtitle = "Houses in Saratoga",
    x = "Age of House",
    y = "Price"
  ) +
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_minimal()
```
Q3: Based on the dataset `SaratogaHouses` from package `mosaicData`,
please draw the boxplot for the house price by number of rooms.

Hint: Transparency of boxplot is specified as `alpha = 0.5`.
```{r}
# Create a boxplot for house prices by the number of rooms
ggplot(SaratogaHouses, aes(x = factor(rooms), y = price)) +
  geom_boxplot(alpha = 0.5, notch = TRUE, fill = "cornflowerblue") +
  labs(
    title = "House price distribution by number of rooms",
    x = "Number of rooms",
    y = "Price"
  ) +
  scale_y_continuous(labels = scales::dollar_format()) +
  theme_minimal()
```
Q4: Please plot the Cleveland dot chart for the percentage of receipts in GDP by country.
The datasset `newgdp` from the package `CGPfunctions` records current receipts of fifteen national governments as a percentage of gross domestic product.
You can read more detail by running the code `??newgdp` in the console.

Hint: Please install the package CGPfunctions if you haven’t installed.
(No need to write the install code in the R code chunk below.) The range of x is (0.2, 0.6).
```{r}
data(newgdp, package = "CGPfunctions")

df <- newgdp %>% 
  filter(Year == "Year1979") %>%
  mutate(GDP = GDP / 100)

ggplot(df, aes(
    x = GDP, 
    y = reorder(Country, GDP)
  )
) +
  geom_segment(
    aes(
      x = 0.2,
      xend = GDP,
      y = reorder(Country, GDP),
      yend = Country
    ),
    color = "grey"
  ) +
  geom_point(color="pink", size=3) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    x = "",
    y = "",
    title = "Percentage of Receipts in GDP by Country"
  ) +
  theme_light() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank()
  )
```